Notes and other text

### 2023-04-18 doc/manuscript/translocation.qmd

Second, repeated translocations and long-term monitoring of naturally recovered populations demonstrate that fitness benefits of robust phenotypes are maintained beyond the natal environment in the presence of Bd.
Specifically, robust phenotypes in recovered populations have reduced infection intensities, below the level known to cause significant host mortality [@vredenburg2010, @knapp2016].
This phenotype persists following translocations to new environments --- translocated populations maintain infection intensities below this threshold and infection intensity is not a significant predictor of adult survival following translocation.
Moreover, high adult survival in the presence of Bd persists into subsequent generations in non-natal environments, suggesting that robust phenotypes are heritable to some degree.
Together, strong selection following disease-induced declines and heritable increases in fitness point to evolutionary rescue as an important driver of observed natural recoveries and host persistence in this system [@knapp2016].
A key advance of our study is that we take these exciting results a step further, leveraging natural evolutionary rescue and translocations to promote MYL frog recovery at the landscape scale.

>>>>

Second, repeated translocations and long-term monitoring of naturally recovered populations demonstrate that fitness benefits of robust phenotypes are maintained beyond the natal environment in the presence of Bd.
Specifically, robust phenotypes in recovered populations have reduced infection intensities, below the level known to cause significant host mortality [@vredenburg2010, @knapp2016].
This phenotype persists following translocations to new environments --- translocated populations maintain infection intensities below this threshold and infection intensity is not a significant predictor of adult survival following translocation.
Moreover, high adult survival in the presence of Bd persists into subsequent generations in non-natal environments, suggesting that robust phenotypes are heritable to some degree.
Together, we show that strong selection following disease-induced declines and heritable increases in fitness point to evolutionary rescue as an important driver of observed natural recoveries and host persistence in this system [@knapp2016].
A key advance of our study is that we take these exciting results a step further, leveraging natural evolutionary rescue and translocations to promote MYL frog recovery at the landscape scale.
